---
title: "CLOSE study analysis"
date: "`r Sys.Date()`"
output:
  rmdformats::material:
    highlight: kate
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="999")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE, results="hide"}
library(plyr)
library(irr)
setwd("C:/Users/alexw/Google Drive/Desktop files/Dal Med/RIM")

```

```{r}
data1=read.csv("Data Collection Form - Final.csv")
data2=read.csv("Data Collection Form_Wong.csv")
data1$version=c("Gold standard")
data2$version=c("MT")
data=rbind(data1, data2)

version=c("Gold standard","MT")

for (ver in version){
  column=c()
  
  dataver=subset(data, data$version==ver)
  
  column=append(column, nrow(dataver))
  
  column=append(column, nrow(subset(dataver, dataver$Gender=="M")))
  column=append(column, nrow(subset(dataver, dataver$Gender=="M"))/nrow(dataver)*100)
  column=append(column, nrow(subset(dataver, dataver$Gender=="F")))
  column=append(column, nrow(subset(dataver, dataver$Gender=="F"))/nrow(dataver)*100)
  
  column=append(column, nrow(subset(dataver, dataver$Keros.Classification..Type.I.III.==1)))
  column=append(column, nrow(subset(dataver, dataver$Keros.Classification..Type.I.III.==1))/nrow(dataver)*100)
  column=append(column, nrow(subset(dataver, dataver$Keros.Classification..Type.I.III.==2)))
  column=append(column, nrow(subset(dataver, dataver$Keros.Classification..Type.I.III.==2))/nrow(dataver)*100)
  column=append(column, nrow(subset(dataver, dataver$Keros.Classification..Type.I.III.==3)))
  column=append(column, nrow(subset(dataver, dataver$Keros.Classification..Type.I.III.==3))/nrow(dataver)*100)
  
  column=append(column, nrow(subset(dataver, dataver$Asymmetry..height.difference.1mm.==1)))
  column=append(column, nrow(subset(dataver, dataver$Asymmetry..height.difference.1mm.==1))/nrow(dataver)*100)
  column=append(column, nrow(subset(dataver, dataver$Asymmetry..height.difference.1mm.==0)))
  column=append(column, nrow(subset(dataver, dataver$Asymmetry..height.difference.1mm.==0))/nrow(dataver)*100)
  
  column=append(column, nrow(subset(dataver, dataver$Bony.dehiscence==1)))
  column=append(column, nrow(subset(dataver, dataver$Bony.dehiscence==1))/nrow(dataver)*100)
  column=append(column, nrow(subset(dataver, dataver$Bony.dehiscence==0)))
  column=append(column, nrow(subset(dataver, dataver$Bony.dehiscence==0))/nrow(dataver)*100)
  
  column=append(column, nrow(subset(dataver, dataver$Intact.lamina==0)))
  column=append(column, nrow(subset(dataver, dataver$Intact.lamina==0))/nrow(dataver)*100)
  column=append(column, nrow(subset(dataver, dataver$Intact.lamina==1)))
  column=append(column, nrow(subset(dataver, dataver$Intact.lamina==1))/nrow(dataver)*100)
  
  column=append(column, nrow(subset(dataver, dataver$Orbital.dehiscence.into.ethmoid.sinus==1)))
  column=append(column, nrow(subset(dataver, dataver$Orbital.dehiscence.into.ethmoid.sinus==1))/nrow(dataver)*100)
  column=append(column, nrow(subset(dataver, dataver$Orbital.dehiscence.into.ethmoid.sinus==0)))
  column=append(column, nrow(subset(dataver, dataver$Orbital.dehiscence.into.ethmoid.sinus==0))/nrow(dataver)*100)
  
  column=append(column, nrow(subset(dataver, dataver$Ucinate.process.contacting.orbital.wall==1)))
  column=append(column, nrow(subset(dataver, dataver$Ucinate.process.contacting.orbital.wall==1))/nrow(dataver)*100)
  column=append(column, nrow(subset(dataver, dataver$Ucinate.process.contacting.orbital.wall==0)))
  column=append(column, nrow(subset(dataver, dataver$Ucinate.process.contacting.orbital.wall==0))/nrow(dataver)*100)
  
  column=append(column, nrow(subset(dataver, dataver$Presence==1)))
  column=append(column, nrow(subset(dataver, dataver$Presence==1))/nrow(dataver)*100)
  column=append(column, nrow(subset(dataver, dataver$Presence==0)))
  column=append(column, nrow(subset(dataver, dataver$Presence==0))/nrow(dataver)*100)
  
  column=append(column, nrow(subset(dataver, dataver$Carotid.dehiscence==1)))
  column=append(column, nrow(subset(dataver, dataver$Carotid.dehiscence==1))/nrow(dataver)*100)
  column=append(column, nrow(subset(dataver, dataver$Carotid.dehiscence==0)))
  column=append(column, nrow(subset(dataver, dataver$Carotid.dehiscence==0))/nrow(dataver)*100)
  
  column=append(column, nrow(subset(dataver, dataver$Optic.nerve.dehiscence==1)))
  column=append(column, nrow(subset(dataver, dataver$Optic.nerve.dehiscence==1))/nrow(dataver)*100)
  column=append(column, nrow(subset(dataver, dataver$Optic.nerve.dehiscence==0)))
  column=append(column, nrow(subset(dataver, dataver$Optic.nerve.dehiscence==0))/nrow(dataver)*100)
  
  column=append(column, nrow(subset(dataver, dataver$Sinus.septation.inserting.on.carotid.canal==1)))
  column=append(column, nrow(subset(dataver, dataver$Sinus.septation.inserting.on.carotid.canal==1))/nrow(dataver)*100)
  column=append(column, nrow(subset(dataver, dataver$Sinus.septation.inserting.on.carotid.canal==0)))
  column=append(column, nrow(subset(dataver, dataver$Sinus.septation.inserting.on.carotid.canal==0))/nrow(dataver)*100)
  
  column=append(column, nrow(subset(dataver, dataver$Supraortibal.pneumatization==1)))
  column=append(column, nrow(subset(dataver, dataver$Supraortibal.pneumatization==1))/nrow(dataver)*100)
  column=append(column, nrow(subset(dataver, dataver$Supraortibal.pneumatization==0)))
  column=append(column, nrow(subset(dataver, dataver$Supraortibal.pneumatization==0))/nrow(dataver)*100)
  
  if (ver=="Gold standard"){
    table1=as.data.frame(column)
  } else{
    table1=cbind(table1, column)
  }
}


colnames(table1)=c("Gold standard","MT")
rownames(table1)=c("n","M","M%","F","F%",
                   "Keros1","Keros1%","Keros2","Keros2%","Keros3","Keros3%",
                   "Y Asym","Y Asym%","N Asym","N Asym%",
                   "Y Bony dehisc","Y Bony dehisc%","N Bony dehisc","N Bony dehisc%",
                   "Y intact lamina","Y Intact lamina%","N intact lamina","N intact lamina%",
                   "Y orbit dehisc","Y orbit dehisc%","N orbit dehisc","N orbit dehisc%",
                   "Y ucinate contact","Y ucinate contact%","N ucinate contact","N ucinate contact%",
                   "Y onodi","Y onodi%","N onodi","N onodi%",
                   "Y carotid dehisc","Y carotid dehisc%","N carotid dehisc","N carotid dehisc%",
                   "Y ON dehisc","Y ON dehisc%","N ON dehisc","N ON dehisc%",
                   "Y sinus sept","Y sinus sept%","N sinus sept","N sinus sept%",
                   "Y supraorb pneum","Y supraorb pneum%","N supraorb pneum","N supraorb pneum%"
                   )

write.csv(table1, "table1.csv")

```
# Table 1
```{r}
table1
```
# Interrater agreement between gold standard and medical traineee

## Cribriform Plate
### Keros classification
```{r}
kappa2(cbind(as.factor(data1$Keros.Classification..Type.I.III.), as.factor(data2$Keros.Classification..Type.I.III.)), "equal")
```
### Asymmetry
```{r}
kappa2(cbind(data1$Asymmetry..height.difference.1mm.,data2$Asymmetry..height.difference.1mm.), "unweighted")
```
### Bony dehiscence
```{r}
kappa2(cbind(data1$Bony.dehiscence,data2$Bony.dehiscence), "unweighted")
```
## Lamina papyracea
### Intact lamina
```{r}
kappa2(cbind(data1$Intact.lamina,data2$Intact.lamina), "unweighted")
```
### Orbital dehiscence into ethmoid sinus
```{r}
kappa2(cbind(data1$Orbital.dehiscence.into.ethmoid.sinus,data2$Orbital.dehiscence.into.ethmoid.sinus), "unweighted")
```
### Ucinate process contacting orbital wall
```{r}
kappa2(cbind(data1$Ucinate.process.contacting.orbital.wall,data2$Ucinate.process.contacting.orbital.wall), "unweighted")
```
## Onodi cell presence

```{r}
kappa2(cbind(data1$Presence,data2$Presence), "unweighted")
```
## Sphenoid sinus
### Carotid artery dehiscence
```{r}
kappa2(cbind(data1$Carotid.dehiscence,data2$Carotid.dehiscence), "unweighted")
```
### Optic nerve dehiscence
```{r}
kappa2(cbind(data1$Optic.nerve.dehiscence,data2$Optic.nerve.dehiscence), "unweighted")
```
### Sinus septation inserting on carotid canal
```{r}
kappa2(cbind(data1$Sinus.septation.inserting.on.carotid.canal,data2$Sinus.septation.inserting.on.carotid.canal), "unweighted")
```
## Ethmoid artery
### Supraorbital pneumatization
```{r}
kappa2(cbind(data1$Supraortibal.pneumatization,data2$Supraortibal.pneumatization), "unweighted")

```