---
title: "Post-ISAT Statistical Analysis"
date: "`r Sys.Date()`"
output:
  rmdformats::material:
    highlight: kate
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="999999")
opts_knit$set(width=75)
```


# Loading files for analysis

```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE, results="hide"}
library(MASS)
library(Hmisc)
library(brant)
library(generalhoslem)
library(DescTools)
library(aod)
library(pROC)
```

```{r}
setwd("C:/Users/alexw/OneDrive/Dal Med/Aneurysm Repair Project/Data Analysis")
data=read.csv("Data table FINAL.csv")
```

# Data Cleaning
### Remove missing values

```{r}
data=subset(data, data$DOB!="NA")
data=subset(data, data$Gender!="NA")
data=subset(data, data$Admission.Date!="NA")
data=subset(data, data$Discharge.Date!="NA")
data=subset(data, data$Current.smoke!="NA")
data=subset(data, data$HTN!="NA")
data=subset(data, data$DM!="NA")
data=subset(data, data$Past.SAH!="NA")
data=subset(data, data$Past.stroke!="NA")
data=subset(data, data$Op.Date!="NA")
data=subset(data, data$Time.to.Treatment..days.!="NA")
data=subset(data, data$SAH.Etiology=="aSAH")
data$SAH.Etiology<-factor(data$SAH.Etiology)
data=subset(data, data$X..Aneurysms!="NA")
data=subset(data, data$A1.size!="NA")
data=subset(data, data$A1.location!="NA")
data$A1.location <- factor(data$A1.location)
data=subset(data, data$WFNS!="NA")
data=subset(data, data$Fisher!="NA")
data=subset(data, data$GOS.at.discharge!="NA")
data=subset(data, data$Length.of.hospital.stay..day.!="NA")
data=subset(data, data$Mortality!="NA")
data=subset(data, data$Rebleed!="NA")
data=subset(data, data$Treatment=="Coil"|data$Treatment=="Clip")
data$Treatment <- factor(data$Treatment, levels=c("Clip","Coil"), ordered=FALSE)

```

### Recategorize aneurysm location to anterior vs posterior circulation
```{r}
data$A1.location=as.character(data$A1.location)
data$A1.location[data$A1.location=="ACA" | 
                 data$A1.location=="Acomm"|
                 data$A1.location=="ICA"|
                 data$A1.location=="MCA"|
                 data$A1.location=="PC"
                 ]="Anterior"
data$A1.location[data$A1.location=="AICA" | 
                 data$A1.location=="BA"|
                 data$A1.location=="PCA"|
                 data$A1.location=="Pcomm"|
                 data$A1.location=="PICA"|
                 data$A1.location=="SCA"|
                 data$A1.location=="VA"|
                 data$A1.location=="VBJ"
                 ]="Posterior"
data$A1.location=as.factor(data$A1.location)
```

# Table 1
```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE, results="hide"}
treattype=c("Coil","Clip")
for(treat in treattype){
  column=c()
  datatreat=subset(data, data[,"Treatment"]==treat)
  
  column=nrow(datatreat)
  column=append(column, round(mean(datatreat$Age.at.admission),digits=1))
  column=append(column, round(sd(datatreat$Age.at.admission),digits=1))
  
  column=append(column, nrow(subset(datatreat, datatreat$Gender=="M")))
  column=append(column, nrow(subset(datatreat, datatreat$Gender=="M"))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$Gender=="F")))
  column=append(column, nrow(subset(datatreat, datatreat$Gender=="F"))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$Current.smoke==1)))
  column=append(column, nrow(subset(datatreat, datatreat$Current.smoke==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$Current.smoke==0)))
  column=append(column, nrow(subset(datatreat, datatreat$Current.smoke==0))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$HTN==1)))
  column=append(column, nrow(subset(datatreat, datatreat$HTN==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$HTN==0)))
  column=append(column, nrow(subset(datatreat, datatreat$HTN==0))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$DM==1)))
  column=append(column, nrow(subset(datatreat, datatreat$DM==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$DM==0)))
  column=append(column, nrow(subset(datatreat, datatreat$DM==0))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$Past.SAH==1)))
  column=append(column, nrow(subset(datatreat, datatreat$Past.SAH==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$Past.SAH==0)))
  column=append(column, nrow(subset(datatreat, datatreat$Past.SAH==0))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$Past.stroke==1)))
  column=append(column, nrow(subset(datatreat, datatreat$Past.stroke==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$Past.stroke==0)))
  column=append(column, nrow(subset(datatreat, datatreat$Past.stroke==0))/nrow(datatreat)*100)
  
  column=append(column, round(mean(datatreat$Time.to.Treatment..days.),digits=1))
  column=append(column, round(sd(datatreat$Time.to.Treatment..days.),digits=1))
  
  column=append(column, nrow(subset(datatreat, datatreat$X..Aneurysms==1)))
  column=append(column, nrow(subset(datatreat, datatreat$X..Aneurysms==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$X..Aneurysms>1)))
  column=append(column, nrow(subset(datatreat, datatreat$X..Aneurysms>1))/nrow(datatreat)*100)
  
  column=append(column, round(mean(datatreat$A1.size),digits=1))
  column=append(column, round(sd(datatreat$A1.size),digits=1))
  
  column=append(column, nrow(subset(datatreat, datatreat$A1.location=="Anterior")))
  column=append(column, nrow(subset(datatreat, datatreat$A1.location=="Anterior"))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$A1.location=="Posterior")))
  column=append(column, nrow(subset(datatreat, datatreat$A1.location=="Posterior"))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$WFNS<4)))
  column=append(column, nrow(subset(datatreat, datatreat$WFNS<4))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$WFNS>=4)))
  column=append(column, nrow(subset(datatreat, datatreat$WFNS>=4))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$Fisher<3)))
  column=append(column, nrow(subset(datatreat, datatreat$Fisher<3))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$Fisher>=3)))
  column=append(column, nrow(subset(datatreat, datatreat$Fisher>=3))/nrow(datatreat)*100)
  
  column=append(column, round(mean(datatreat$Length.of.hospital.stay..day.),digits=1))
  column=append(column, round(sd(datatreat$Length.of.hospital.stay..day.),digits=1))
  
  if (treat=="Coil"){
    table1=as.data.frame(column)
  }else{
    table1=cbind(table1, column)
  }
}
colnames(table1)=c("Coil","Clip")
rownames(table1)=c("n",
                   "Mean Age at Admission","SD Age at Admission",
                   "M","M %",
                   "F","F %",
                   "Y Smoke","Y Smoke %",
                   "N Smoke","N Smoke %",
                   "Y HTN","Y HTN %",
                   "N HTN","N HTN %",
                   "Y DM","Y DM %",
                   "N DM","N DM %",
                   "Y PastSAH","Y PastSAH %",
                   "N PastSAH","N PastSAH %",
                   "Y stroke","Y stroke %",
                   "N stroke","N stroke %",
                   "Mean Time to treat (d)","SD Time to Treat",
                   "Single aneurysm", "% single aneurysm",
                   "Multiple aneurysms","% multiple aneurysms",
                   "Mean Culprit Aneurysm Size (mm)","SD Culprit Aneurysm Size",
                   "Anterior location","Anterior location %",
                   "Posterior location","Posterior location %",
                   "WFNS 1-3","WFNS 1-3 %",
                   "WFNS 4-5","WFNS 4-5 %",
                   "Fisher 1-2","Fisher 1-2 %",
                   "Fisher 3-4","Fisher 3-4 %",
                   "Mean Length of hospital stay (d)","SD Length of hospital stay (d)"
                   )
```

```{r}
print(table1)
```

# Table 1 statistics
### Mean Age at Admission

```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE, results="hide"}
datacoil=subset(data, data$Treatment=="Coil")
dataclip=subset(data, data$Treatment=="Clip")
```

```{r}
data$Treatment <- droplevels(data$Treatment)
t.test(Age.at.admission ~ Treatment, data=data)
```

### Gender
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$Gender=="M")),nrow(subset(datacoil, datacoil$Gender=="F"))),
                 c(nrow(subset(dataclip, dataclip$Gender=="M")),nrow(subset(dataclip, dataclip$Gender=="F")))
                 ))
chisq.test(M)
```

### Current smoking
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$Current.smoke==1)),nrow(subset(datacoil, datacoil$Current.smoke==0))),
                 c(nrow(subset(dataclip, dataclip$Current.smoke==1)),nrow(subset(dataclip, dataclip$Current.smoke==0)))
                 ))
chisq.test(M)
```

### Hypertension
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$HTN==1)),nrow(subset(datacoil, datacoil$HTN==0))),
                 c(nrow(subset(dataclip, dataclip$HTN==1)),nrow(subset(dataclip, dataclip$HTN==0)))
))
chisq.test(M)
```

### Diabetes Mellitus
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$DM==1)),nrow(subset(datacoil, datacoil$DM==0))),
                 c(nrow(subset(dataclip, dataclip$DM==1)),nrow(subset(dataclip, dataclip$DM==0)))
))
chisq.test(M)
```

### Prior aneurysm repair
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$Past.SAH==1)),nrow(subset(datacoil, datacoil$Past.SAH==0))),
                 c(nrow(subset(dataclip, dataclip$Past.SAH==1)),nrow(subset(dataclip, dataclip$Past.SAH==0)))
))
fisher.test(M)
```

### Prior stroke
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$Past.stroke==1)),nrow(subset(datacoil, datacoil$Past.stroke==0))),
                 c(nrow(subset(dataclip, dataclip$Past.stroke==1)),nrow(subset(dataclip, dataclip$Past.stroke==0)))
))
fisher.test(M)
```

### Time to treatment
```{r}
t.test(Time.to.Treatment..days. ~ Treatment, data=data)
```

### Single vs multiple aneurysms
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$X..Aneurysms==1)),nrow(subset(datacoil, datacoil$X..Aneurysms>1))),
                 c(nrow(subset(dataclip, dataclip$X..Aneurysms==1)),nrow(subset(dataclip, dataclip$X..Aneurysms>1)))
))
chisq.test(M)
```

### Mean culprit aneurysm size
```{r}
t.test(A1.size ~ Treatment, data=data)
```

### Aneurysm location
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$A1.location=="Anterior")),nrow(subset(datacoil, datacoil$A1.location=="Posterior"))),
                 c(nrow(subset(dataclip, dataclip$A1.location=="Anterior")),nrow(subset(dataclip, dataclip$A1.location=="Posterior")))
))
chisq.test(M)
```

### WFNS
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$WFNS<4)),nrow(subset(datacoil, datacoil$WFNS>=4))),
                 c(nrow(subset(dataclip, dataclip$WFNS<4)),nrow(subset(dataclip, dataclip$WFNS>=4)))
))
chisq.test(M)
```

### Fisher
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$Fisher<3)),nrow(subset(datacoil, datacoil$Fisher>=3))),
                 c(nrow(subset(dataclip, dataclip$Fisher<3)),nrow(subset(dataclip, dataclip$Fisher>=3)))
))
chisq.test(M)
```

### Length of hospital stay
```{r}
t.test(Length.of.hospital.stay..day. ~ Treatment, data=data)
```

# Outcome Table
```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE, results="hide"}
for(treat in treattype){
  column=c()
  datatreat=subset(data, data[,"Treatment"]==treat)
  
  column=append(column, nrow(subset(datatreat, datatreat$GOS.at.discharge==1)))
  column=append(column, nrow(subset(datatreat, datatreat$GOS.at.discharge==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$GOS.at.discharge==2|datatreat$GOS.at.discharge==3)))
  column=append(column, nrow(subset(datatreat, datatreat$GOS.at.discharge==2|datatreat$GOS.at.discharge==3))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$GOS.at.discharge==4|datatreat$GOS.at.discharge==5)))
  column=append(column, nrow(subset(datatreat, datatreat$GOS.at.discharge==4|datatreat$GOS.at.discharge==5))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$Mortality==1)))
  column=append(column, nrow(subset(datatreat, datatreat$Mortality==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$Mortality==0)))
  column=append(column, nrow(subset(datatreat, datatreat$Mortality==0))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$Rebleed==1)))
  column=append(column, nrow(subset(datatreat, datatreat$Rebleed==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$Rebleed==0)))
  column=append(column, nrow(subset(datatreat, datatreat$Rebleed==0))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$Vasospasm==1)))
  column=append(column, nrow(subset(datatreat, datatreat$Vasospasm==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$Vasospasm==0)))
  column=append(column, nrow(subset(datatreat, datatreat$Vasospasm==0))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$Infarct==1)))
  column=append(column, nrow(subset(datatreat, datatreat$Infarct==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$Infarct==0)))
  column=append(column, nrow(subset(datatreat, datatreat$Infarct==0))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$Hydrocephalus==1)))
  column=append(column, nrow(subset(datatreat, datatreat$Hydrocephalus==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$Hydrocephalus==0)))
  column=append(column, nrow(subset(datatreat, datatreat$Hydrocephalus==0))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$Seizure==1)))
  column=append(column, nrow(subset(datatreat, datatreat$Seizure==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$Seizure==0)))
  column=append(column, nrow(subset(datatreat, datatreat$Seizure==0))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$Infection==1)))
  column=append(column, nrow(subset(datatreat, datatreat$Infection==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$Infection==0)))
  column=append(column, nrow(subset(datatreat, datatreat$Infection==0))/nrow(datatreat)*100)
  
  column=append(column, nrow(subset(datatreat, datatreat$Pneumonia==1)))
  column=append(column, nrow(subset(datatreat, datatreat$Pneumonia==1))/nrow(datatreat)*100)
  column=append(column, nrow(subset(datatreat, datatreat$Pneumonia==0)))
  column=append(column, nrow(subset(datatreat, datatreat$Pneumonia==0))/nrow(datatreat)*100)
  
  if (treat=="Coil"){
    outcomes=as.data.frame(column)
  }else{
    outcomes=cbind(outcomes, column)
  }
}

colnames(outcomes)=c("Coil","Clip")
rownames(outcomes)=c("GOS 1","GOS 1 %","GOS 2-3","GOS 2-3 %","GOS-4-5","GOS 4-5 %",
                     "Y Mortality","Y Mortality %",
                     "N Mortality","N Mortality %",
                     "Y Rebleed","Y Rebleed %",
                     "N Rebleed","N Rebleed %",
                     "Y Vasospasm","Y Vasospasm %",
                     "N Vasospasm","N Vasospasm %",
                     "Y Infarct","Y Infarct %",
                     "N Infarct","N Infarct %",
                     "Y Hydrocephalus","Y Hydrocephalus %",
                     "N Hydrocephalus","N Hydrocephalus %",
                     "Y Seizure","Y Seizure %",
                     "N Seizure","N Seizure %",
                     "Y Infection","Y Infection %",
                     "N Infection","N Infection %",
                     "Y Pneumonia","Y Pneumonia %",
                     "N Pneumonia","N Pneumonia %")
```

```{r}
print(outcomes)
```

# Outcome Statistics

### GOS at discharge
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$GOS.at.discharge==1)),
                   nrow(subset(datacoil,(datacoil$GOS.at.discharge==2|datacoil$GOS.at.discharge==3))),
                   nrow(subset(datacoil, datacoil$GOS.at.discharge==4|datacoil$GOS.at.discharge==5))),
                 c(nrow(subset(dataclip, dataclip$GOS.at.discharge==1)),
                   nrow(subset(dataclip,(dataclip$GOS.at.discharge==2|dataclip$GOS.at.discharge==3))),
                   nrow(subset(dataclip, dataclip$GOS.at.discharge==4|dataclip$GOS.at.discharge==5)))
))
chisq.test(M)
```

### Mortality
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$Mortality=="1")),nrow(subset(datacoil, datacoil$Mortality=="0"))),
                 c(nrow(subset(dataclip, dataclip$Mortality=="1")),nrow(subset(dataclip, dataclip$Mortality=="0")))
))
chisq.test(M)
```

### Rebleed
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$Rebleed=="1")),nrow(subset(datacoil, datacoil$Rebleed=="0"))),
                 c(nrow(subset(dataclip, dataclip$Rebleed=="1")),nrow(subset(dataclip, dataclip$Rebleed=="0")))
))
chisq.test(M)
```

### Vasospasm
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$Vasospasm=="1")),nrow(subset(datacoil, datacoil$Vasospasm=="0"))),
                 c(nrow(subset(dataclip, dataclip$Vasospasm=="1")),nrow(subset(dataclip, dataclip$Vasospasm=="0")))
))
chisq.test(M)
```

### Infarct
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$Infarct=="1")),nrow(subset(datacoil, datacoil$Infarct=="0"))),
                 c(nrow(subset(dataclip, dataclip$Infarct=="1")),nrow(subset(dataclip, dataclip$Infarct=="0")))
))
chisq.test(M)
```

### Hydrocephalus
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$Hydrocephalus=="1")),nrow(subset(datacoil, datacoil$Hydrocephalus=="0"))),
                 c(nrow(subset(dataclip, dataclip$Hydrocephalus=="1")),nrow(subset(dataclip, dataclip$Hydrocephalus=="0")))
))
chisq.test(M)
```

### Seizure
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$Seizure=="1")),nrow(subset(datacoil, datacoil$Seizure=="0"))),
                 c(nrow(subset(dataclip, dataclip$Seizure=="1")),nrow(subset(dataclip, dataclip$Seizure=="0")))
))
fisher.test(M)
```

### Infection
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$Infection=="1")),nrow(subset(datacoil, datacoil$Infection=="0"))),
                 c(nrow(subset(dataclip, dataclip$Infection=="1")),nrow(subset(dataclip, dataclip$Infection=="0")))
))
fisher.test(M)
```

### Pneumonia
```{r}
M=as.table(cbind(c(nrow(subset(datacoil, datacoil$Pneumonia=="1")),nrow(subset(datacoil, datacoil$Pneumonia=="0"))),
                 c(nrow(subset(dataclip, dataclip$Pneumonia=="1")),nrow(subset(dataclip, dataclip$Pneumonia=="0")))
))
fisher.test(M)
```

# GOS Regression Analyses
### Recategorize GOS
```{r}
#Recategorize GOS.at.discharge to dead, dependent, and independent
data$GOS.at.discharge=as.character(data$GOS.at.discharge)
data$GOS.at.discharge[data$GOS.at.discharge=="1"]=0
data$GOS.at.discharge[data$GOS.at.discharge=="2"|data$GOS.at.discharge=="3"]=1
data$GOS.at.discharge[data$GOS.at.discharge=="4"|data$GOS.at.discharge=="5"]=2
data$GOS.at.discharge=as.factor(data$GOS.at.discharge)
data$GOS.at.discharge <- factor(data$GOS.at.discharge, levels=c(0,1,2), ordered=FALSE)
```

### Recategorize age
```{r}
#Recategorize age into <50 and >=50
data$Age.at.admission0=c(0)
data$Age.at.admission1=c(0)
data$Age.at.admission0[data$Age.at.admission<50]=1
data$Age.at.admission1[data$Age.at.admission>=50]=1
data$Age.at.admission1 <- factor(data$Age.at.admission1, levels=c(0,1), ordered=FALSE)
```

```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE, results="hide"}
data$HTN <- factor(data$HTN, levels=c(0,1), ordered=FALSE)
```

### Crude models

##### Treatment (Coil vs Clip)
```{r message=FALSE}
modeltreatment <- polr(GOS.at.discharge ~ Treatment, data = data, Hess=TRUE)
ctable <- coef(summary(modeltreatment))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable <- cbind(ctable, "p value" = p)
ci <- confint(modeltreatment)
modeltreatment
exp(coef(modeltreatment))
exp(rbind(OR = coef(modeltreatment), ci))
```

##### Hypertension
```{r message=FALSE}
modelhtn <- polr(GOS.at.discharge ~ HTN, data = data, Hess=TRUE)
ctable <- coef(summary(modelhtn))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable <- cbind(ctable, "p value" = p)
ci <- confint(modelhtn)
modelhtn
exp(coef(modelhtn))
exp(rbind(OR = coef(modelhtn), ci))
```

##### Age
```{r message=FALSE}
modelage <- polr(GOS.at.discharge ~ Age.at.admission1, data = data, Hess=TRUE)
ctable <- coef(summary(modelage))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable <- cbind(ctable, "p value" = p)
ci <- confint(modelage)
modelage
exp(coef(modelage))
exp(rbind(OR = coef(modelage), ci))
```

### Adjusted model

```{r message=FALSE}
modeladjusted <- polr(GOS.at.discharge ~ Treatment + HTN + Age.at.admission1, data = data, Hess=TRUE)
ctable <- coef(summary(modeladjusted))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable <- cbind(ctable, "p value" = p)
ci <- confint(modeladjusted)
modeladjusted
exp(coef(modeladjusted))
exp(cbind(OR = coef(modeladjusted), ci))
PseudoR2(modeladjusted, which="all")
```

### Diagnostics for adjusted model

##### Confusion matrix to calculate misclassification rate
```{r}
predictGOS = predict(modeladjusted,data)
table(data$GOS.at.discharge, predictGOS)
mean(as.character(data$GOS.at.discharge) != as.character(predictGOS))
```

##### Brant test for proportional odds assumption
```{r warning=FALSE}
brant(modeladjusted)
```

##### Goodness of fit tests
```{r}
logitgof(data$GOS.at.discharge, fitted(modeladjusted), g = 10, ord = TRUE)
lipsitz.test(modeladjusted)
pulkrob.chisq(modeladjusted, c("Treatment"))
pulkrob.deviance(modeladjusted, c("Treatment"))
```

# Secondary outcomes regression analyses

### Mortality

##### Crude model
```{r warning=FALSE, message=FALSE, error=FALSE}
data$Mortality <- factor(data$Mortality, levels=c(0,1), ordered=FALSE)
modelmort=glm(Mortality ~ Treatment, data=data, family="binomial")
summary(modelmort)
exp(coef(modelmort))
exp(cbind(OR = coef(modelmort), confint(modelmort)))
```

##### Adjusted model
```{r warning=FALSE, message=FALSE, error=FALSE}
modelmort=glm(Mortality ~ Treatment + HTN + Age.at.admission1, data=data, family="binomial")
summary(modelmort)
exp(coef(modelmort))
exp(cbind(OR = coef(modelmort), confint(modelmort)))
logitgof(data$Mortality, fitted(modelmort))
rocmort=roc(data$Mortality, predict(modelmort,type=c("response")), ci=TRUE, auc=TRUE)
plot.roc(rocmort, print.auc=TRUE, xlim=c(1,0), xlab="1-Specificity", asp=NA)
```

### Rebleed

##### Crude model
```{r warning=FALSE, message=FALSE, error=FALSE}
data$Rebleed <- factor(data$Rebleed, levels=c(0,1), ordered=FALSE)
modelrebleed=glm(Rebleed ~ Treatment, data=data, family="binomial")
summary(modelrebleed)
exp(coef(modelrebleed))
exp(cbind(OR = coef(modelrebleed), confint(modelrebleed)))
```

##### Adjusted model
```{r warning=FALSE, message=FALSE, error=FALSE}
modelrebleed=glm(Rebleed ~ Treatment + HTN + Age.at.admission1, data=data, family="binomial")
summary(modelrebleed)
exp(coef(modelrebleed))
exp(cbind(OR = coef(modelrebleed), confint(modelrebleed)))
logitgof(data$Rebleed, fitted(modelrebleed))
rocrebleed=roc(data$Rebleed, predict(modelrebleed,type=c("response")), ci=TRUE, auc=TRUE)
plot.roc(rocrebleed, print.auc=TRUE, xlim=c(1,0), xlab="1-Specificity", asp=NA)
```

### Vasospasm

##### Crude model
```{r warning=FALSE, message=FALSE, error=FALSE}
data$Vasospasm <- factor(data$Vasospasm, levels=c(0,1), ordered=FALSE)
modelvasospasm=glm(Vasospasm ~ Treatment, data=data, family="binomial")
summary(modelvasospasm)
exp(coef(modelvasospasm))
exp(cbind(OR = coef(modelvasospasm), confint(modelvasospasm)))
```

##### Adjusted model
```{r warning=FALSE, message=FALSE, error=FALSE}
modelvasospasm=glm(Vasospasm ~ Treatment + HTN + Age.at.admission1, data=data, family="binomial")
summary(modelvasospasm)
exp(coef(modelvasospasm))
exp(cbind(OR = coef(modelvasospasm), confint(modelvasospasm)))
logitgof(data$Vasospasm, fitted(modelvasospasm))
rocvasospasm=roc(data$Vasospasm, predict(modelvasospasm,type=c("response")), ci=TRUE, auc=TRUE)
plot.roc(rocvasospasm, print.auc=TRUE, xlim=c(1,0), xlab="1-Specificity", asp=NA)
```

### Infarct

##### Crude model
```{r warning=FALSE, message=FALSE, error=FALSE}
data$Infarct <- factor(data$Infarct, levels=c(0,1), ordered=FALSE)
modelinfarct=glm(Infarct ~ Treatment, data=data, family="binomial")
summary(modelinfarct)
exp(coef(modelinfarct))
exp(cbind(OR = coef(modelinfarct), confint(modelinfarct)))
```

##### Adjusted model
```{r warning=FALSE, message=FALSE, error=FALSE}
modelinfarct=glm(Infarct ~ Treatment + HTN + Age.at.admission1, data=data, family="binomial")
summary(modelinfarct)
exp(coef(modelinfarct))
exp(cbind(OR = coef(modelinfarct), confint(modelinfarct)))
logitgof(data$Infarct, fitted(modelinfarct))
rocinfarct=roc(data$Infarct, predict(modelinfarct,type=c("response")), ci=TRUE, auc=TRUE)
plot.roc(rocinfarct, print.auc=TRUE, xlim=c(1,0), xlab="1-Specificity", asp=NA)
```

### Hydrocephalus

##### Crude model
```{r warning=FALSE, message=FALSE, error=FALSE}
data$Hydrocephalus <- factor(data$Hydrocephalus, levels=c(0,1), ordered=FALSE)
modelhydro=glm(Hydrocephalus ~ Treatment, data=data, family="binomial")
summary(modelhydro)
exp(coef(modelhydro))
exp(cbind(OR = coef(modelhydro), confint(modelhydro)))
```

##### Adjusted model
```{r warning=FALSE, message=FALSE, error=FALSE}
modelhydro=glm(Hydrocephalus ~ Treatment + HTN + Age.at.admission1, data=data, family="binomial")
summary(modelhydro)
exp(coef(modelhydro))
exp(cbind(OR = coef(modelhydro), confint(modelhydro)))
logitgof(data$Hydrocephalus, fitted(modelhydro))
rochydro=roc(data$Hydrocephalus, predict(modelhydro,type=c("response")), ci=TRUE, auc=TRUE)
plot.roc(rochydro, print.auc=TRUE, xlim=c(1,0), xlab="1-Specificity", asp=NA)
```

### Seizure

##### Crude model
```{r warning=FALSE, message=FALSE, error=FALSE}
data$Seizure <- factor(data$Seizure, levels=c(0,1), ordered=FALSE)
modelseize=glm(Seizure ~ Treatment, data=data, family="binomial")
summary(modelseize)
exp(coef(modelseize))
exp(cbind(OR = coef(modelseize), confint(modelseize)))
```

##### Adjusted model
```{r warning=FALSE, message=FALSE, error=FALSE}
modelseize=glm(Seizure ~ Treatment + HTN + Age.at.admission1, data=data, family="binomial")
summary(modelseize)
exp(coef(modelseize))
exp(cbind(OR = coef(modelseize), confint(modelseize)))
logitgof(data$Seizure, fitted(modelseize))
rocseize=roc(data$Seizure, predict(modelseize,type=c("response")), ci=TRUE, auc=TRUE)
plot.roc(rocseize, print.auc=TRUE, xlim=c(1,0), xlab="1-Specificity", asp=NA)
```

### Infection

##### Crude model
```{r warning=FALSE, message=FALSE, error=FALSE}
data$Infection <- factor(data$Infection, levels=c(0,1), ordered=FALSE)
modelinfect=glm(Infection ~ Treatment, data=data, family="binomial")
summary(modelinfect)
exp(coef(modelinfect))
exp(cbind(OR = coef(modelinfect), confint(modelinfect)))
```

##### Adjusted model
```{r warning=FALSE, message=FALSE, error=FALSE}
modelinfect=glm(Infection ~ Treatment + HTN + Age.at.admission1, data=data, family="binomial")
summary(modelinfect)
exp(coef(modelinfect))
exp(cbind(OR = coef(modelinfect), confint(modelinfect)))
logitgof(data$Infection, fitted(modelinfect))
rocinfect=roc(data$Infection, predict(modelinfect,type=c("response")), ci=TRUE, auc=TRUE)
plot.roc(rocinfect, print.auc=TRUE, xlim=c(1,0), xlab="1-Specificity", asp=NA)
```

### Pneumonia

##### Crude model
```{r warning=FALSE, message=FALSE, error=FALSE}
data$Pneumonia <- factor(data$Pneumonia, levels=c(0,1), ordered=FALSE)
modelpneum=glm(Pneumonia ~ Treatment, data=data, family="binomial")
summary(modelpneum)
exp(coef(modelpneum))
exp(cbind(OR = coef(modelpneum), confint(modelpneum)))
```

##### Adjusted model
```{r warning=FALSE, message=FALSE, error=FALSE}
modelpneum=glm(Pneumonia ~ Treatment + HTN + Age.at.admission1, data=data, family="binomial")
summary(modelpneum)
exp(coef(modelpneum))
exp(cbind(OR = coef(modelpneum), confint(modelpneum)))
logitgof(data$Pneumonia, fitted(modelpneum))
rocpneum=roc(data$Pneumonia, predict(modelpneum,type=c("response")), ci=TRUE, auc=TRUE)
plot.roc(rocpneum, print.auc=TRUE, xlim=c(1,0), xlab="1-Specificity", asp=NA)
```







